\section{Test with Users}
\label{sec:test}

\subsection{Experiment Design}
The experiments we performed have two parts:\\

\begin{itemize}
	\item \textbf{Gesture Control and Collision Avoidance}: To test this part the tester has to teleoperate MASHI using our gesture control system and perform some simple tasks, going out of the laboratory room and coming back. The testers are also asked to try to collide and interact with the environment so they could test the effectiveness of the collision system. After the test the tester has to answer a short survey about the user friendliness and the efficiency of our system.
	
	\item \textbf{Vital Space}: In the second and last part of the test we focus on the personal distance the users feel good interacting with the robot. We ask the users what is the distance to the robot they feel comfortable with and try approaching the robot to them.
\end{itemize}

The small survey consists of the following 10 questions:

\begin{enumerate}
	\item The system is easy to use. (Disagree 1 to 5 Totally Agree)
	\item The system is intuitive. (Disagree 1 to 5 Totally Agree)
	\item The system responds accordingly to your expectations. (Disagree 1 to 5 Totally Agree)
	\item What would you improve from the system?
	\item The gesture commands are easy and intuitive. (Disagree 1 to 5 Totally Agree)
	\item Which gesture is more complicated to detect?
	\item Which improvement do you think would be interesting for the gesture control?
	\item The anti-collision system is useful. (Disagree 1 to 5 Totally Agree)
	\item Do you think the speed reduction is useful?
	\item After the test, at which distance you consider the robot must stop in order to avoid a collision with a human?
\end{enumerate}





\subsection{Experiment Results}